Enrich the datasets with new columns.

### 2020-08-21 inst/analysis/enrich_dataset.Rmd
Optimizations

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.4/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.4/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

```{r}
eval_calls_base <- eval_calls_base %>% count(across(c(-eval_call_id, -starts_with("caller_stack"))), name = "nb_eval_calls") 
eval_calls <- eval_calls %>% count(across(c(-eval_call_id)), name = "nb_eval_calls")
```

```{r}
eval_calls_base <- eval_calls_base %>% 
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)

eval_calls <- eval_calls %>% 
    mutate(eval_call_package = extract_package_name(eval_call_srcref, file)) %>% 
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)
```

```{r}
#eval_calls <- eval_calls %>% mutate(parse_args = if_else(is.na(expr_parsed_expression), NA, map_chr(expr_parsed_expression, extract_args_parse)))
```

```{r write_back}
write_fst(eval_calls, paste0(params$data_dirpath, "deduplicated_calls.fst"))

write_fst(eval_calls_base, paste0(params$data_dirpath, "base_calls.fst"))
```

>>>>

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.5/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

```{r}
eval_calls_base <- eval_calls_base %>% 
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)
```

```{r}
eval_calls_base <- eval_calls_base %>% count(across(c(-eval_call_id, -starts_with("caller_stack"))), name = "nb_eval_calls") 
eval_calls_dedup <- eval_calls %>% count(across(c(-eval_call_id)), name = "nb_eval_calls")
eval_calls_dedup_more <- eval_calls %>% count(across(c(-eval_call_id, -starts_with("caller_stack"))), name = "nb_eval_calls") 
```

```{r}
eval_calls <- eval_calls_dedup_more %>% mutate(parse_args = if_else(is.na(expr_parsed_expression), NA, map_chr(expr_parsed_expression, extract_args_parse)))
```

```{r}
eval_calls_dedup_more <- eval_calls_dedup_more %>% mutate(eval_call_package = map2_chr(eval_call_srcref, file, extract_package_name)) 
```

```{r}
eval_calls_dedup_more <- eval_calls_dedup_more %>% 
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)
```

```{r write_back}
write_fst(eval_calls_dedup, paste0(params$data_dirpath, "deduplicated_calls.fst"))

write_fst(eval_calls_dedup_more, paste0(params$data_dirpath, "deduplicated_more_calls.fst"))

write_fst(eval_calls_base, paste0(params$data_dirpath, "base_calls.fst"))

write_fst(eval_calls, paste0(params$data_dirpath, "enriched_calls.fst"))
```
